---
title: "EDS241: Final"
author: "Jake Eisaguirre"
date: '`r format(Sys.time(), "%m/%d/%Y")`'
output: 
  pdf_document:
    toc: false
    number_sections: yes
header-includes:
  - \setlength{\parindent}{1em}
  - \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

librarian::shelf(tidyverse, here, janitor, estimatr, broom, kableExtra)
```

##### Clean Data

```{r}

data <- read_csv(here("KM_EDS241.csv"))

```

##### (a)

\noindent Using the data for 1981, estimate a simple OLS regression of real house values on the
indicator for being located near the incinerator in 1981. What is the house value “penalty” for
houses located near the incinerator? Does this estimated coefficient correspond to the ‘causal’
effect of the incinerator (and the negative amenities that come with it) on housing values?
Explain why or why not.

```{r}
data_81 <- data %>% 
  filter(year == 1981)

mod1 <- lm_robust(rprice ~ nearinc, data = data_81)

```

```{r}
tidy(mod1) %>%
  kable()
```


##### (b)

\noindent Using the data for 1978, provide some evidence the location choice of the incinerator was
not “random”, but rather selected on the basis of house values and characteristics. [Hint: in the
1978 sample, are house values and characteristics balanced by nearinc status?]

```{r}
data_78 <- data %>% 
  filter(year == 1978)

mod2 <- lm_robust(nearinc ~  rprice + rooms + area + year + land + age, data = data_78)

tidy(mod2) %>%
  kable()
```


##### (c)

\noindent Based on the observed differences in (b), explain why the estimate in (a) is likely to be
biased downward (i.e., overstate the negative effect of the incinerator on housing values).

```{r}

```


##### (d)

\noindent Use a difference-in-differences (DD) estimator to estimate the causal effect of the incinerator on housing values without controlling for house and lot characteristics. Interpret the magnitude and sign of the estimated DD coefficient. 

```{r}

```


##### (e)

\noindent Report the 95% confidence interval for the estimate of the causal effect on the incinerator in (d). 

```{r}

```


##### (f)

\noindent How does your answer in (d) changes when you control for house and lot characteristics?
Test the hypothesis that the coefficients on the house and lot characteristics are all jointly equal
to 0.

```{r}

```


##### (g)

\noindent Using the results from the DD regression in (f), calculate by how much did real housing
values change on average between 1978 and 1981.

```{r}

```


##### (h)

\noindent  Explain (in words) what is the key assumption underlying the causal interpretation of the DD estimator in the context of the incinerator construction in North Andover.

```{r}

```

